GxHash: A High-Throughput, Non-Cryptographic Hashing Algorithm Leveraging Modern CPU Capabilities

### 2023-11-18 article/article.tex
Fix typo in article

Once the state's bits have been thoroughly mixed, the next step is to reduce this state into a smaller, fixed-size hash output, typically 32 or 64 bits. There are several approaches to this, one being combiniting the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance). GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the four rounds of AES. This allow the GxHash algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.

@@

    The avalanche effect can be computed by flipping a single random bit for a given input and checking the differences between the hashes generated before and after the bit was flipped. Ideally, half of the bit should change on average.
    \item \textbf{Performance:} The performance of a noncryptographic hash function is usually reflected by the performance of the application using it. For instance, a fast non-cryptographic hash function generally implies a fast hash table. This specific criteria will be tackled in the next section which is dedicated to it.

>>>>

Once the state's bits have been thoroughly mixed, the next step is to reduce this state into a smaller, fixed-size hash output, typically 32 or 64 bits. There are several approaches to this, one being combining the \( X \)-bit integer parts of the mixed state together (by xoring them together for instance). GxHash takes a simpler path by reinterpreting our state into a smaller \( X \)-bit value, assuming an uniform distribution at the mixing stage thanks to the four rounds of AES. This allow the GxHash algorithm to generate hashes of any size up to \( s_b \) bits with virtually no additional computational cost.

@@

    The avalanche effect can be computed by flipping a single random bit for a given input and checking the differences between the hashes generated before and after the bit was flipped. Ideally, half of the hash bits should change on average.
    \item \textbf{Performance:} The performance of a noncryptographic hash function is usually reflected by the performance of the application using it. For instance, a fast non-cryptographic hash function generally implies a fast hash table. This specific criteria will be tackled in the next section which is dedicated to it.
